---
title: "Hydrologic_metrics"
author: "tn"
date: "10/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(sf)
library(leaflet)
library(ggplot2)
library(readxl)
library(foreign)
library(dataRetrieval)
library(waterData)
library(lfstat)
library(plotly)
library(FlowScreen)
library(hydrostats)
library(lfstat)
library(scales)
library(zoo)

```

#Load in data
See urban greenness_gagesII_selection.Rmd for study gage filtering and downloading of daily hydro data

```{r}
#list of study gages and cathcment characterisitcs
gage_filter_ld<- read.csv("G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Data\\Hydro_data\\study_catchments_oct6.csv", colClasses = c("STAID"="character"))

#annual discharge volume for all gages (calculated in 'urban greenness_gagesII_selection.Rmd')
all_gage_annual_runoff_ld<- read.csv( "G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\Annual_runoff_watyr.csv", colClasses=c("STAID"="character"))

#daily mean discharge for all gages
all_gage_bind_ld <- read.csv( "G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\daily_runoff.csv", colClasses=c("STAID"="character", "site_no"="character")) %>%mutate(Date=as.Date(Date))
```


```{r eval=FALSE, include=FALSE}
#daily max data for where we have it
all_gage_max_bind_ld<-read.csv("G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\daily_max_runoff.csv", colClasses=("site_no"="character")) %>%mutate(Date=as.Date(Date))

#join daily means to daily maxs
all_gage_meanmax<- left_join(all_gage_bind_ld, all_gage_max_bind_ld, by = c("Date" = "Date", "site_no" = "site_no" ))

```

# all_gage_annual_runoff_ld will serve as master dataset summarised to year
#Set rule for inclusion of year as complete year for annual discharge metric
complete > 90% of days have flow data. = 328.5 days

```{r}
#complete>328 days
all_gage_annual_runoff_ld <- all_gage_annual_runoff_ld %>% mutate(complete =ifelse(n>328, 1, 0))
```


#Calulate high flow metrics
```{r}
#calc monthly medians from the mean daily. Used to determine high flow treshhold
all_gage_bind_ld<-renameNWISColumns(all_gage_bind_ld)

all_gage_bind_ld<- all_gage_bind_ld %>% mutate(month = substr(Date, 6,7),
                                               day=substr(Date, 9,10),
                                               Date=as.character(Date),
                                               Date=as.POSIXct(Date,format="%Y-%m-%d"))

mnth_med_allyrs <- all_gage_bind_ld %>% group_by(site_no, month) %>% summarise(mnth_med_allyrs= median(Flow))

mnth_med_curyr <- all_gage_bind_ld %>% group_by(site_no, month, year) %>% summarise(mnth_med_curyr= median(Flow))

all_gage_bind_ld <- all_gage_bind_ld %>% left_join(mnth_med_allyrs, by = c("month" = "month", "site_no" = "site_no" )) %>% left_join (mnth_med_curyr, by = c("month" = "month", "site_no" = "site_no", "year" = "year")) 

#head(all_gage_meanmax)

```

```{r}
#calculate high flow metric. (And annual CV)
#All of these calculations use daily mean flow. we only have daily max flow for 122 sites and limited years for those sites

#define peaks. threshold = 3x monthly median flow. calculated using local and global threshold
all_gage_bind_ld <- all_gage_bind_ld %>% 
  mutate(Peak_global =ifelse(Flow>(3*mnth_med_allyrs), 1, 0),
         Peak_local =ifelse(Flow>(3*mnth_med_curyr), 1, 0))

#annual peak stats - global threshold
annual_hi_glob <- all_gage_bind_ld %>% filter(Peak_global==1) %>% group_by(STAID, wat_yr) %>% summarise(Hi_flow_days_glob = sum(Peak_global), Hi_flow_avg_glob=mean(Flow))

length(unique(annual_hi_glob$STAID))

#annual peak stats - local threshold
annual_hi_loc <- all_gage_bind_ld %>% filter(Peak_local==1) %>% group_by(STAID, wat_yr) %>% summarise(Hi_flow_days_loc = sum(Peak_local), Hi_flow_avg_loc =mean(Flow))

length(unique(annual_hi_glob$STAID))

#annual CV
annual_cv <- all_gage_bind_ld %>% group_by(STAID, wat_yr) %>% summarise(CV=(sd(Flow, na.rm=TRUE)/ mean(Flow, na.rm=TRUE)*100))



#join high flow metrics together
all_gage_annual_hi_flow<- left_join(annual_hi_glob, annual_hi_loc, by = c("STAID" = "STAID", "wat_yr" = "wat_yr")) %>% left_join(annual_cv, by = c("STAID" = "STAID", "wat_yr" = "wat_yr"))


```

#trying different hydro packages
```{r eval=FALSE, include=FALSE}
#tried to use flowsceen package but it would not accpt my data as time series

save(all_gage_bind_ld, file= "flows.Rdata")
flowscreen <- read.flows("flows.Rdata")
flow_ts <- create.ts(flowscreen,  hyrstart = 10)
```

```{r}
# formating data for hydrostats package

reformat<-all_gage_bind_ld%>% mutate(Date=as.character(Date))
flow_ts<-ts.format(reformat, format="%Y-%m-%d", cols=c(4,5))
col_order <- c("Date", "Q", "site_no", 'wat_yr')
flow_ts<-flow_ts[, col_order] #changing column order
flow_ts$Q <- replace(flow_ts$Q, which(flow_ts$Q < 0), NA) #replacing negative flows with NA
```

#calculate baseflows 

```{r}
##using hydrostats

#split data into list of data frames for each gage. REMOVE gage with all NAs #419 in list and gage number 04084445
flow_list <- split(flow_ts, f = flow_ts$site_no)
flow_list <- flow_list[-419]

#apply baseflow funtion to one item in list
baseflow_test <- baseflows(flow_list[[1]], ts ="daily") #this works for one gage

#apply baseflow funtion to all gage sites
baseflow<-lapply(flow_list, baseflows, ts='daily') #this works!

#getting gage number assigned back to data and collapse to single data frame. Also adding in peak flow thresholds here based on bf
baseflow_df<-dplyr::bind_rows(baseflow, .id = "site_no") %>% 
  mutate(wat_yr = water_year(Date, origin=10),
         bf_x3 = bf*3,
         bf_x2 = bf*2,
         bf_x1_5=bf*1.5,
         Date=as.character(Date),
         Date=as.POSIXct(Date,format="%Y-%m-%d"))

all_gage_annual_baseflow <- baseflow_df %>% group_by(site_no, wat_yr) %>% summarise(annual_avg_bf =mean(bf, na.rm = TRUE))

```

```{r eval=FALSE, include=FALSE}
# Baseflows works using lfstat pkg too. but we will stick with hydrostats

#calc vector of bfs
baseflow_test_values <- baseflow(flow_ts$Q)

#Bind vector back to data
baseflow_ts <- cbind(flow_ts,baseflow_test_values)

#calculate mean bf per year
all_gage_annual_baseflow <- baseflow_ts %>% group_by(site_no, wat_yr) %>% summarise(annual_avg_baseflow =mean(baseflow_test_values, na.rm = TRUE))

```


#calculate peaks flows
 Could not find a way to identify peaks that does not require a threshold. We use high flow spells funtion from hydro stats to define peak flows.Here I create some new thresholds and plot them to see which looks best. 15 day moving median looks best (med_15).

```{r}
#create Moving window median thresholds

flow_ts <- flow_ts %>% group_by(site_no)%>% mutate(
  med_30=rollapply(Q,30, median, fill=Q),
  med_15=rollapply(Q,15, median, fill=Q)) %>% ungroup()
```


```{r}
ts_plots<-left_join(baseflow_df, all_gage_bind_ld, by = c("Date" = "Date", "site_no" = "site_no" )) %>%  left_join(flow_ts, by = c("Date" = "Date", "site_no" = "site_no" ))%>%
  mutate(global_3x_mth_med=3*mnth_med_allyrs,
         local_3x_mnth_med=3*mnth_med_curyr)
```


```{r, fig.height = 10, fig.asp = .62}
#some hydrograph plots with thresholds

ts_plots %>% filter(site_no =='01096500', wat_yr.x==2015) %>% pivot_longer(cols =c(Q, bf, global_3x_mth_med, local_3x_mnth_med, bf_x2,  med_30, med_15), names_to='metric')%>%
  ggplot(aes(Date, value, group=metric, colour=metric)) +
    geom_line() +
      ggtitle("hydrograph for gage 01096500")+
  xlab('')+
  ylab("daily mean flow (cfs)")+
  theme(axis.text.x = element_text(angle = 90, hjust=0))+
  scale_x_datetime(breaks = date_breaks(width = "10 days"), labels = date_format("%b-%d"))

  
ts_plots %>% filter(site_no =='01094400', wat_yr.x==c(1995,2005)) %>% pivot_longer(cols =c(Q, global_3x_mth_med, local_3x_mnth_med, med_15), names_to='metric')%>%
  ggplot(aes(Date, value, group=metric, colour=metric)) +
    geom_line() +
  facet_wrap(~ wat_yr.x, scales="free_x", nrow=2)+
  xlab('')+
  ylab("daily mean flow (cfs)")+
  scale_x_datetime(breaks = date_breaks(width = "10 days"), labels = date_format("%b-%d"))+
  theme_bw()+
    theme(axis.text.x = element_text(angle = 90, hjust=0))


```

```{r}
#calculate high spells

test_01094400 <- flow_ts %>% filter(site_no =='01094400')

reformat<-test_01094400%>% mutate(Date=as.character(Date))
test_ts<-ts.format(reformat, format="%Y-%m-%d", cols=c(1,2))


high_spells <- high.spells(test_ts, quant = NULL, threshold = test_ts$med_15, ind.days = 5,  duration = TRUE, volume = TRUE, plot = TRUE, ignore.zeros = FALSE,
ctf.threshold = 0.1, ann.stats = TRUE, ann.stats.only = FALSE, inter.flood = FALSE,
hydro.year=FALSE)


```

