---
title: "Stream gages for evaluating impacts of urban greeness"
author: "tn"
date: "8/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
library(sf)
library(leaflet)
library(ggplot2)
library(readxl)
library(foreign)
library(dataRetrieval)
library(waterData)
library(lfstat)
library(plotly)
```


## Load gage data

```{r}
#gage data from gagesII dataset (basin info, landcover, flow record info, and other, from 2009)

basinid <- read_excel("X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\gagesII_additionaldata\\gagesII_sept30_2011_conterm.xlsx", sheet= "BasinID", col_names=TRUE)

flowrec <- read_excel("X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\gagesII_additionaldata\\gagesII_sept30_2011_conterm.xlsx", sheet= "FlowRec", col_names=TRUE) %>%
  select(1:6)

lc_basin <- read_excel("X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\gagesII_additionaldata\\gagesII_sept30_2011_conterm.xlsx", sheet= "LC06_Basin", col_names=TRUE) %>%
  select(1:4)

climate<-read_excel("X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\gagesII_additionaldata\\gagesII_sept30_2011_conterm.xlsx", sheet= "Climate", col_names=TRUE) %>%
  select(1,2)
  
infra<-read_excel("X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\gagesII_additionaldata\\gagesII_sept30_2011_conterm.xlsx", sheet= "Pop_Infrastr", col_names=TRUE) %>%
  select(1,7)

topo<-read_excel("X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\gagesII_additionaldata\\gagesII_sept30_2011_conterm.xlsx", sheet= "Topo", col_names=TRUE) %>%
  select(1,10)

gage<-left_join(basinid, lc_basin,  by='STAID') %>%
  left_join(., flowrec, by='STAID') %>%
  left_join(., climate, by='STAID') %>%
  left_join(., infra, by='STAID') %>%
  left_join(., topo, by='STAID')
```

```{r}
#gage data from NHD gage.info dataset (includes active gages in 2015)

gageinfo <- read.dbf("X:\\Staff Files\\Data\\GISDATA\\Tyler_GISDATA\\NHD\\NHDPlusNationalData\\GageInfo.dbf") %>%
  select(1,6,7, 10)

#join to gage
gage<- left_join(gage, gageinfo, by=c('STAID'='GAGEID'))


```

```{r}
#join updated landcover attributes

LC<- read.table("G:\\.shortcut-targets-by-id\\1mXpuIifC_L0FfJk0j2Vz-Hw8yJ2IqiSj\\Urban Greeness Tracking Research\\Analysis\\BasinSummary.txt", sep=',', header =TRUE,  colClasses=c("SITE_NO"="character"))

LC2<- read.table("G:\\.shortcut-targets-by-id\\1mXpuIifC_L0FfJk0j2Vz-Hw8yJ2IqiSj\\Urban Greeness Tracking Research\\Analysis\\BasinSummary.txt", sep=",")


#%>% mutate(STAID=as.character(SITE_NO))
#gage<-gage%>% mutate(SITE_NO=as.numeric(STAID))

gage<-left_join(gage, LC, by= c('STAID'='SITE_NO'))

#test<-left_join(LC, gage, by= c('SITE_NO'='STAID'))
#count(test, STANAME=='NA')

```

#compare landcover
```{r}
ggplot(gage, aes(IMPNLCD06, NLCD2016_I)) +
    geom_point(colour="black", fill="white")

ggplot(gage, aes(NLCD2001_I, NLCD2016_I)) +
    geom_point(colour="black", fill="white")
```



# basin filtering
```{r}
##filter criteria counts
#active in 2015
count(gage, Active==1) #6,624

#old selection criteria with old data set
count(gage, Active==1 & DASqMi < 20 & DEVNLCD06 > 25) #336 (less data using gagesII dataset 332vs516 )

#active in 2015 and at least 10 years data since 1990
count(gage, Active==1 & FLOWYRS_1990_2009>10) #4,822

##active in 2015 area < 25 sqmi
count(gage, Active==1 & DASqMi < 25) #985

##active in 2015 and at least 10 years data since 1990 & area < 25 sqmi
count(gage, Active==1 & FLOWYRS_1990_2009>10 & DASqMi < 25) #550

##active in 2015 and data to 1990 & area < 25 sqmi & %DEVELOPED > 25
count(gage, Active==1 & FLOWYRS_1990_2009>10 & DASqMi < 25 & DEVNLCD06 > 25) # 200

##active in 2015 and data to 1990 & area < 25 sqmi & %IMPERVIOUS > 25
count(gage, Active==1 & FLOWYRS_1990_2009>10 & DASqMi > 0 & IMPNLCD06 > 5) # 607
count(gage, Active==1 & FLOWYRS_1990_2009>10 & DASqMi > 0 & NLCD2016_I > 5) # 819


query<-filter(gage, Active==1 & FLOWYRS_1990_2009>10 & DASqMi > 0 & IMPNLCD06 > 5) # 169

count(gage, NLCD2016_I == 5)

##filter dataset
gage_filter <- filter(gage, Active==1 & FLOWYRS_1990_2009>10 & DASqMi > 0 & NLCD2016_I > 5)
```

# manually add in 2nd nature cities
```{r eval=FALSE, include=FALSE}
add_countieslist<-c('Prince Georges', 'Philadelphia', 'Milwaukee', 'Maricopa', 'Los Angeles', 'Monterey', 'Dist Of Columbia', 'District of Columbia')
  
add_counties<-filter(gage, COUNTYNAME_SITE %in% add_countieslist)

add_counties <- filter(add_counties, Active==1 & FLOWYRS_1990_2009>10 & DASqMi < 200 & IMPNLCD06 > 5)

#join to others
gage_filter <- bind_rows (gage_filter, add_counties)
gage_filter <- unique(gage_filter)
```

#download recent gage data
```{r}

gagelist<- gage_filter$STAID

head(gagelist)

parameterCd <- "00060"  # Discharge
startDate <- "2010-01-01"  
endDate <- "2019-12-31"

#these take forever
#test_discharge <- readNWISuv(gagelist[1], parameterCd,  startDate, endDate)

#dailys avg are faster but not what we want. but can use to exclude gages without enough history
#test_daily<- readNWISdv(gagelist[1], parameterCd,  startDate, endDate)

#downloading dailies for all gaes under 20 sqr miles.
all_daily_2010 <- lapply(gagelist, readNWISdv, parameterCd, startDate, endDate)

```

#calculate number of recent years on record
```{r}
#calculate # of years of record since 1980

#make year collumn
all_daily_2010_yr<- lapply(all_daily_2010, function(x) mutate(x, year = substr(x$Date, 1,4)))

all_daily_2010_yr<- lapply(all_daily_2010_yr, function(x) mutate(x, STAID = as.factor(x$site_no)))


#get number of records per year - summarise by year and count
all_yr_count <- lapply(all_daily_2010_yr, function(x) count(x, STAID, year))

#if > 364 = complete year
all_yr_count <- lapply(all_yr_count, function(x) mutate(x, complete =ifelse(x$n>360, 1, 0)))

#merge tables
all_yr_countbind <- dplyr::bind_rows(all_yr_count)

#summerise number of complete years per gage since 2010
all_10yr_count <- all_yr_countbind %>% group_by(STAID) %>% summarise(FLOWYRS_2010_2019 = sum(complete))

#join to gage short list
gage_filter<- left_join(gage_filter, all_10yr_count, by='STAID')

```

#filter again to gages with > 7yrs recent data
```{r}

gage_filter<- filter(gage_filter, FLOWYRS_2010_2019>7)


#export to CSV
#first make another collumn to preserve actual gageID
gage_filter <- gage_filter %>% mutate(STAID_STRG=paste("`",STAID))

write.csv(gage_filter, "C:\\Users\\tnodi\\Desktop\\data\\TNC_project\\study_gages_sept11.csv")

#exporting as csv converts STAID to numberic which alters the value. need a work around to join to basins.
```

#rank number of gages by county
```{r}

county_rank <- gage_filter %>% count(COUNTYNAME_SITE, STATE) %>%
  rename('n_gages'='n')%>%
  arrange(desc(n_gages))

county_rank

state_rank <- gage_filter %>% count(STATE) %>%
  rename('n_gages'='n')%>%
  arrange(desc(n_gages))

state_rank

#export as csv for GSI data inquires
write.csv(county_rank, "X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\county_gages_studyfilter.csv")

write.csv(state_rank, "X:\\Urban_greeness_research\\Data\\Hydro\\Gagedata\\Study_gages_City_rank.csv")
```


Map the gage locations
```{r}
#make interactive map to show gage locations in cities

m <- leaflet(data = gage_filter) %>% 
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addCircleMarkers(~LNG_GAGE,~LAT_GAGE, radius = 2, popup =paste("Name:", gage_filter$STANAME, "<br>",
                           "Drainage area:", gage_filter$DASqMi, "sqmi", "<br>",
                           "% Impervious:", gage_filter$IMPNLCD06))



m  # Print the map


```

```{r}
#make some distribution plots based on filter criteria
ggplot(gage_filter, aes(x=DASqMi)) +
    geom_histogram(binwidth=2, colour="black", fill="white")+
  xlab("Drainage area (sqmi)")+
    scale_y_continuous(breaks=c(2,4,6,8,10))

ggplot(gage_filter, aes(x=NLCD2016_I)) +
    geom_histogram(binwidth=1, colour="black", fill="white")+
    xlab("% Impervious")+
    scale_y_continuous(breaks=c(2,4,6,8,10))

```

```{r}
#make some distribution plots based on characteristics
ggplot(gage_filter, aes(x=PPTAVG_BASIN)) +
    geom_histogram(binwidth=2, colour="black", fill="white")+
  xlab("Avg annual rainfall (cm)")+
  scale_y_continuous(breaks=c(2,4,6,8,10))

ggplot(gage_filter, aes(x=SLOPE_PCT)) +
    geom_histogram(binwidth=0.25, colour="black", fill="white")+
    xlab("Avg slope (%)")+
    scale_y_continuous(breaks=c(2,4,6,8,10))


```



#now download all the hydro data

```{r eval=FALSE, include=FALSE}

parameterCd <- "00060"  # Discharge
startDate <- "1980-01-01"  
endDate <- "2019-12-31"



#downloading dailies for all to 1980.
all_daily_1980 <- lapply(gagelist, readNWISdv, parameterCd, startDate, endDate)
```

```{r eval=FALSE, include=FALSE}

#make year collumn
all_daily_1980_yr<- lapply(all_daily_1980, function(x) mutate(x, year = substr(x$Date, 1,4)))
all_daily_1980_yr<- lapply(all_daily_1980_yr, function(x) mutate(x, STAID = as.factor(x$site_no)))


#combine all gages 
all_gage_bind <- dplyr::bind_rows(all_daily_1980_yr)

#calc discharge per day and assign water year
all_gage_bind <- all_gage_bind %>% mutate(cf_day = X_00060_00003*86400,
                                          STAID = as.factor(site_no),
                                          wat_yr = water_year(Date, origin=10))



#sum runoff per year
all_gage_annual_runoff <- all_gage_bind %>% group_by(STAID, wat_yr) %>% summarise(cf_yr = sum(cf_day))
length(unique(all_gage_annual_runoff$STAID))


# calc complete years
all_yr_count2 <- all_gage_bind %>% count(site_no, wat_yr)
#if > 360 = complete year
all_yr_count2 <- all_yr_count2 %>% mutate(complete =ifelse(n>360, 1, 0),
                                          STAID = as.factor(site_no))




#join to annual runoff data. remove years without full record
all_gage_annual_runoff<- left_join(all_gage_annual_runoff, all_yr_count2, by = c("STAID" = "STAID", "wat_yr" = "wat_yr"))

all_gage_annual_runoff_complete<-filter(all_gage_annual_runoff, complete == 1 )

write.csv(all_gage_annual_runoff, "G:\\.shortcut-targets-by-id\\1mXpuIifC_L0FfJk0j2Vz-Hw8yJ2IqiSj\\Urban Greeness Tracking Research\\Analysis\\Annual_runoff_watyr.csv")

write.csv(all_gage_bind, "G:\\.shortcut-targets-by-id\\1mXpuIifC_L0FfJk0j2Vz-Hw8yJ2IqiSj\\Urban Greeness Tracking Research\\Analysis\\daily_runoff.csv")

```

#join flow data to other data
```{r eval=FALSE, include=FALSE}
#sumarise_annual_runoff
mean_annual_runoff<-all_gage_annual_runoff %>% group_by(STAID) %>% summarise(mean_annual_runoff=mean(cf_yr)) 

gage_filter<-left_join(gage_filter, mean_annual_runoff, by="STAID")

gage_filter<-gage_filter %>% mutate(MAR_stand= mean_annual_runoff/DASqMi)

write.csv(gage_filter, "G:\\.shortcut-targets-by-id\\1mXpuIifC_L0FfJk0j2Vz-Hw8yJ2IqiSj\\Urban Greeness Tracking Research\\Data\\Hydro_data\\study_catchments_oct6.csv")

write.table(gage_filter, "G:\\.shortcut-targets-by-id\\1mXpuIifC_L0FfJk0j2Vz-Hw8yJ2IqiSj\\Urban Greeness Tracking Research\\Data\\Hydro_data\\study_catchments_oct6.txt")

```

```{r}
#list of study gages and cathcment characterisitcs
gage_filter_ld<- read.csv("G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Data\\Hydro_data\\study_catchments_oct6.csv", colClasses = c("STAID"="character"))

#annual discharge volume for all gages (calculated in 'urban greenness_gagesII_selection.Rmd')
all_gage_annual_runoff_ld<- read.csv( "G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\Annual_runoff_watyr.csv", colClasses=c("STAID"="character"))

#daily mean discharge for all gages
all_gage_bind_ld <- read.csv( "G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\daily_runoff.csv", colClasses=c("STAID"="character", "site_no"="character")) %>%mutate(Date=as.Date(Date))

#daily max data for where we have it
all_gage_max_bind_ld<-read.csv("G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\daily_max_runoff.csv", colClasses=("site_no"="character")) %>%mutate(Date=as.Date(Date))


#all_gage_bind_ld<-all_gage_bind_ld%>%mutate(Date=as.Date(Date))
```


#plots
```{r}

ggplot(gage_filter_ld, aes(x=MAR_stand)) +
    geom_histogram(colour="black", fill="white")+
    xlab("MAR")

ggplot(gage_filter_ld, aes(NLCD2016_I, MAR_stand)) +
    geom_point(colour="black", fill="white")

ggplot(gage_filter_ld, aes(Prism30n_p, MAR_stand)) +
    geom_point(colour="black", fill="white")+
  xlab("mean annual precip (mm)")+
  ylab("mean annual runoff (cubic ft / by drainage area)")

```


#download daily maxima!
```{r}

gagelist<- gage_filter_ld$STAID


parameterCd <- "00060"  # Discharge
startDate <- "1980-10-01"  
endDate <- "2019-09-30"
statCd <- "00001"

head(gagelist)


#downloading max dailies for all to 1980.
peak_test <- readNWISpeak(gagelist[1], "2018-09-30", endDate)


all_dailymax_1980 <- lapply(gagelist, readNWISdv, parameterCd, startDate, endDate, statCd)

```

```{r}
#combine all gages 
all_dailymax_bind <- dplyr::bind_rows(all_dailymax_1980)
length(unique(all_dailymax_bind$site_no))


#join daily max to daily 

all_gage_meanmax<- left_join(all_gage_bind_ld, all_dailymax_bind, by = c("Date" = "Date", "site_no" = "site_no" ))

write.csv(all_dailymax_bind, "G:\\Shared drives\\2NDNATURE\\Science\\Research Projects\\TNC Urban Greeness Tracking\\Analysis\\daily_max_runoff.csv")
```


```{r}
#calc monthly medians from the mean daily
all_gage_meanmax<-renameNWISColumns(all_gage_meanmax)
head(all_gage_meanmax)

all_gage_meanmax<- all_gage_meanmax %>% mutate(month = substr(Date, 6,7),
                                               day=substr(Date, 9,10))

mnth_med_allyrs <- all_gage_meanmax %>% group_by(site_no, month) %>% summarise(mnth_med_allyrs= median(Flow))

mnth_med_curyr <- all_gage_meanmax %>% group_by(site_no, month, year) %>% summarise(mnth_med_curyr= median(Flow))

all_gage_meanmax <- all_gage_meanmax %>% left_join(mnth_med_allyrs, by = c("month" = "month", "site_no" = "site_no" )) %>% left_join (mnth_med_curyr, by = c("month" = "month", "site_no" = "site_no", "year" = "year"))

#head(all_gage_meanmax)

```

```{r}
#calculate peaks
all_gage_meanmax <- all_gage_meanmax %>% 
  mutate(Peak =ifelse(Flow_Max>(3*mnth_med_allyrs), 1, 0),
        meanPeak =ifelse(Flow>(3*mnth_med_allyrs), 1, 0),
        Peak_local=ifelse(Flow_Max>(3*mnth_med_curyr), 1, 0),
        meanPeak_local =ifelse(Flow>(3*mnth_med_curyr), 1, 0))

#peak stats for all years
all_gage_annual_max <- all_gage_meanmax %>% filter(Peak==1) %>% group_by(STAID, wat_yr) %>% summarise(pk_per_yr = sum(Peak), pk_yr_avg=mean(Flow_Max), pk_yr_med=median(Flow_Max), cv=(sd(Flow_Max, na.rm=TRUE)/
   mean(Flow_Max, na.rm=TRUE)*100))

length(unique(all_gage_annual_max$STAID))

# calc complete years
Flow_Max_yr_count <- all_gage_meanmax %>% filter(Flow_Max>=0) %>% count(site_no, wat_yr)
#if > 360 = complete year
Flow_Max_yr_count <- Flow_Max_yr_count %>% mutate(complete =ifelse(n>360, 1, 0),
                                          STAID = as.factor(site_no))

#join to annual runoff data. remove years without full record
all_gage_annual_max<- left_join(all_gage_annual_max, Flow_Max_yr_count, by = c("STAID" = "STAID", "wat_yr" = "wat_yr"))

all_gage_peak_complete<-filter(all_gage_annual_max, complete == 1 )
```


#join flow data to other data
```{r}
#sumarise_peak_runoff
catchment_peak_runoff<-all_gage_peak_complete %>% group_by(STAID) %>% summarise(pk_per_yr = mean(pk_per_yr), pk_yr_avg=mean(pk_yr_avg), pk_yr_med=mean(pk_yr_med), cv=mean(cv)) 

gage_filter_peak<-left_join(gage_filter_ld, catchment_peak_runoff, by="STAID")

#gage_filter<-gage_filter %>% mutate(MAR_stand= mean_annual_runoff/DASqMi)

```

#plots
```{r}
ggplot(gage_filter_peak, aes(x=pk_per_yr)) +
    geom_histogram(colour="black", fill="white")+
    xlab("MAR")

ggplot(gage_filter_peak, aes(NLCD2016_I, pk_per_yr)) +
    geom_point(colour="black", fill="white")

ggplot(gage_filter_peak, aes(Prism30n_p, pk_per_yr)) +
    geom_point(colour="black", fill="white")

ggplot(gage_filter_peak, aes(NLCD2016_I, cv)) +
    geom_point(colour="black", fill="white")

```

```{r}
#try getting max for select missing gages
gagetest_null<-"01092000"
gagetest2<-c("08072300","01092000", "08072730")

parameterCd <- "00060"  # Discharge
startDate <- "2000-10-01"  
endDate <- "2019-09-30"
statCd <- c("00003","00001", "00002", "00008"	)

maxtest_null<- readNWISdv(gagetest_null,parameterCd, startDate, endDate, statCd)
maxtest_value <- readNWISdv(gagetest2,parameterCd, startDate, endDate, statCd)

peak_test <- readNWISpeak(gagetest_null, "2018-09-29", "2019-09-30")

maxtest_null<-importDVs("01092000", code = "00060", "00001", sdate = startDate,
edate = endDate)

#data availbility
siteNumber = "08072300"
availableData <- whatNWISdata(siteNumber = gagelist, service = c("dv","uv"), parameterCd = "00060")
```


```{r}
availableData %>% filter(data_type_cd=="dv", parm_cd=="00060", stat_cd=="00001") %>%
 ggplot(aes(x=begin_date)) +
    geom_histogram(colour="black", fill="white")

availableData %>% count(data_type_cd=="dv" & parm_cd=="00060" & stat_cd=="00001")

availableData %>% filter(data_type_cd=="uv", parm_cd=="00060") %>%
 ggplot(aes(x=begin_date)) +
    geom_histogram(colour="black", fill="white")

availableData %>% count(data_type_cd=="uv"& parm_cd=="00060")

availableData %>% filter(data_type_cd=="dv", parm_cd=="00060", stat_cd=="00003") %>%
 ggplot(aes(x=begin_date)) +
    geom_histogram(colour="black", fill="white")

availableData %>% count(data_type_cd=="dv"& parm_cd=="00060"& stat_cd=="00003")

```


```{r}
#downloading intantaneous data for all to 1980.
uv_2000 <- lapply(gagelist, readNWISuv, parameterCd, startDate, endDate)

```

###sub analysis looking at effect of using daily max or daily mean

```{r}
metric_comp<-all_gage_meanmax %>% mutate(meanmax_dif= Flow_Max - Flow) %>% filter(Flow_Max>0)


metric_comp_sum <- metric_comp  %>%  mutate(peak_flow_max=ifelse(Peak==1, Flow_Max, 0),
                                            peak_flow_mean=ifelse(meanPeak==1, Flow, 0),
                                            peak_flow_max_loc=ifelse(Peak_local==1, Flow_Max, 0),
                                            peak_flow_mean_loc=ifelse(meanPeak_local==1, Flow, 0)) %>%
 group_by(site_no, wat_yr) %>% 
   summarise(diff=mean(meanmax_dif),
             pk_per_yr=sum(Peak),
             pk_per_yr2=sum(meanPeak),
             pk_yr_avg= mean(peak_flow_max),
             pk_yr_avg2= mean(peak_flow_mean),
             pk_per_yr_loc=sum(Peak_local),
             pk_per_yr2_loc=sum(meanPeak_local),
             pk_yr_avg_loc= mean(peak_flow_max_loc),
             pk_yr_avg2_loc= mean(peak_flow_mean_loc))
```

#Plots comparing peak metrics using max and mean using global paek threshold
```{r}
#plot compare diff metrics across all sites and years

ggplot(metric_comp_sum, aes(pk_per_yr, pk_per_yr2)) +
    geom_point(colour="black", fill="white")

ggplot(metric_comp_sum, aes(pk_yr_avg, pk_yr_avg2)) +
    geom_point(colour="black", fill="white")+
  xlim(0,5000)+
  ylim(0,5000)


#look for single site at differences in peak values

#site 02087275

metric_comp_sum %>% filter(site_no =='02087275') %>% pivot_longer(cols =c(pk_per_yr, pk_per_yr2), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()


metric_comp_sum %>% filter(site_no =='02087275') %>% pivot_longer(cols =c(pk_yr_avg, pk_yr_avg2), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()

#site 02087275

metric_comp_sum %>% filter(site_no =='02168504') %>% pivot_longer(cols =c(pk_per_yr, pk_per_yr2), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()


metric_comp_sum %>% filter(site_no =='02168504') %>% pivot_longer(cols =c(pk_yr_avg, pk_yr_avg2), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()
```

#Plots comparing peak metrics using max and mean using local peak threshold
```{r}
#plot compare diff metrics across all sites and years

ggplot(metric_comp_sum, aes(pk_per_yr_loc, pk_per_yr2_loc)) +
    geom_point(colour="black", fill="white")+
  xlab("peaks per year (using daily max")+
  ylab("peaks per year (using daily mean")+
  xlim(0,150)+
  ylim(0,150)+
  coord_fixed()

ggplot(metric_comp_sum, aes(pk_yr_avg_loc, pk_yr_avg2_loc)) +
    geom_point(colour="black", fill="white")+
  xlab("annual avg peak flow (using daily max)")+
  ylab("annual avg peak flow (using daily mean)")+
  xlim(0,3000)+
  ylim(0,3000)+
  coord_fixed()


#look for single site at differences in peak values

#site 02087275

metric_comp_sum %>% filter(site_no =='02087275') %>% pivot_longer(cols =c(pk_per_yr_loc, pk_per_yr2_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
  ggtitle("peaks per year for gage 02087275")+
  xlab("year")+
  ylab("peaks per year")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using daily max", "using daily mean"), values = c("red", "blue"))


metric_comp_sum %>% filter(site_no =='02087275') %>% pivot_longer(cols =c(pk_yr_avg_loc, pk_yr_avg2_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
    ggtitle("annual avg peak flow for gage 02087275")+
  xlab("year")+
  ylab("annual avg peak flow (cfs)")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using daily max", "using daily mean"), values = c("red", "blue"))

#site 02168504

metric_comp_sum %>% filter(site_no =='02168504') %>% pivot_longer(cols =c(pk_per_yr_loc, pk_per_yr2_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
    ggtitle("peaks per year for gage 02168504")+
  xlab("year")+
  ylab("peaks per year")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using daily max", "using daily mean"), values = c("red", "blue"))


metric_comp_sum %>% filter(site_no =='02168504') %>% pivot_longer(cols =c(pk_yr_avg_loc, pk_yr_avg2_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
      ggtitle("annual avg peak flow for gage 02168504")+
  xlab("year")+
  ylab("annual avg peak flow (cfs)")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using daily max", "using daily mean"), values = c("red", "blue"))

```


#Plots comparing peak metrics using global and local peak threshold for max
```{r}
#plot compare diff metrics across all sites and years

ggplot(metric_comp_sum, aes(pk_per_yr, pk_per_yr_loc)) +
    geom_point(colour="black", fill="white")+
  xlab("peaks per year (using global threshold")+
  ylab("peaks per year (using local threshold")+
  xlim(0,300)+
  ylim(0,300)+
  coord_fixed()

ggplot(metric_comp_sum, aes(pk_yr_avg, pk_yr_avg_loc)) +
    geom_point(colour="black", fill="white")+
  xlab("annual avg peak flow (using global threshold)")+
  ylab("annual avg peak flow (using local threshold)")+
  xlim(0,5000)+
  ylim(0,5000)+
  coord_fixed()


#look for single site at differences in peak values

#site 02087275

metric_comp_sum %>% filter(site_no =='02087275') %>% pivot_longer(cols =c(pk_per_yr, pk_per_yr_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
  ggtitle("peaks per year for gage 02087275")+
  xlab("year")+
  ylab("peaks per year")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using global threshold", "using local threshold"), values = c("red", "blue"))


metric_comp_sum %>% filter(site_no =='02087275') %>% pivot_longer(cols =c(pk_yr_avg, pk_yr_avg_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
    ggtitle("annual avg peak flow for gage 02087275")+
  xlab("year")+
  ylab("annual avg peak flow (cfs)")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using global threshold", "using local threshold"), values = c("red", "blue"))

#site 02087275

metric_comp_sum %>% filter(site_no =='02168504') %>% pivot_longer(cols =c(pk_per_yr, pk_per_yr_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
    ggtitle("peaks per year for gage 02168504")+
  xlab("year")+
  ylab("peaks per year")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using global threshold", "using local threshold"), values = c("red", "blue"))


metric_comp_sum %>% filter(site_no =='02168504') %>% pivot_longer(cols =c(pk_yr_avg, pk_yr_avg_loc), names_to='method')%>%
  ggplot(aes(wat_yr, value, group=method, colour=method)) +
    geom_line() +
    geom_point()+
      ggtitle("annual avg peak flow for gage 02168504")+
  xlab("year")+
  ylab("annual avg peak flow (cfs)")+
  theme(axis.text.x = element_text(angle = 45))+
  scale_color_manual(labels = c("using global threshold", "using local threshold"), values = c("red", "blue"))
```

